Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-18 draft.Rmd
Update draft.Rmd

Worker mobility is a key strategy for improving outcomes like wages and conditions. Routinely, authors show that workers make significant gains through quitting or securing promotions. Despite this, capitalist countries differ in their rates of job mobility; especially in rates of voluntary mobility. Authors typically explain these differences as differences in the freedom to hire or fire workers (Brown) or a differences in the rate of job creation and destruction (OECD). This article argues that mobility rates also differ due to the rewards they offer to workers. More specifically, we propose that countries differ in the rewards tied to quits and promotions.

The aim of the article is two-fold. First, we explicitly compare internal and external mobility as a means to improve eanings growth. Second, we compare this relationship under two different institutional settings, coordinated Germany and the liberal UK (Hall and Soskice, Thelen). Both aims stem from two wrinkles often found in the job mobility literature. The first is authors' tendency to ignore internal promotions as a form of voluntary mobility. Internal promotion are the main form of mobility desired by workers, yet authors often confine mobility types to external quits. Second, is the over-reliance on single case studies. Authors exploring the impact of mobility often use single country exmaples despite the fact that european labour markets are highly divided. Our article highlights this nuance by explicitly comparing quits and promotions in two different institutional settings.

>>>>

Worker mobility is a key strategy for improving earnings and conditions. Routinely, authors show how workers can make significant gains through quitting or securing promotions. Yet, capitalist countries differ in mobility rates; especially in terms of voluntary mobility. If quitting for new employer is more common in the UK than Germany, does this mean that German workers are held back from advancing their careers, or does it mean that the nature of quitting is different in both countries? Authors typically rationalise differences in job mobility as a difference in the freedom to hire or fire workers (Brown) or a difference in job creation and destruction (OECD). This article proposes that German and British institutions shape not only the likelihood of job mobility, but also the rewards tied to mobility.

The aim of the article is two-fold. First, we explicitly compare internal and external mobility as a means to improve earnings growth. Second, we compare this relationship under two different institutional settings, coordinated Germany and the liberal UK (Hall and Soskice, Thelen). Both aims stem from two wrinkles often found in the job mobility literature. First, authors' often ignore internal promotion as a form of voluntary mobility. Internal promotion is the main form of mobility desired by workers, yet we often focus on external quits. Second, is the over-reliance on single case studies. Authors exploring the impact of mobility often use single country exmaples despite the fact that european labour markets are highly divided. Our article highlights this nuance by explicitly comparing quits and promotions in two different institutional settings.
